Shallow EDSLs and Object-Oriented Programming

### 2016-06-21 paper/sections/Interpretations.tex
Minor changes

Before giving an example of dependent interpretations, we first show how to add new
constructs. The new constructs are: \emph{stretch ns c} which inserts additional wires into the circuit \emph{c} by
summing up \emph{ns} and $above\ c_1\ c_2$ which combines two circuits of the same width vertically.
\setlength{\grammarindent}{5em} % increase separation between LHS/RHS
The extended grammar is given below:
%\lstinputlisting[linerange=39-40]{./code/shallowCircuit.hs}%APPLY:SYNTAX_TYPES
\begin{grammar}
<circuit> ::= \ldots
\alt `above' <circuit> <circuit>
\alt `stretch' <positive-numbers> <circuit>
\end{grammar}

Figure~\ref{code:variant} shows how to add new constructs - just defining new classes that implement \lstinline{Circuit}.
\begin{figure}
\lstinputlisting[linerange=2-11]{../src/width/Variants.scala}%APPLY:VARIANT_SCALA
\caption{Adding new language constructs}
\label{code:variant}
\end{figure}
\paragraph{Solving the Expression Problem (EP)} As EDSLs evolve along the time, the
demand of new syntax and new semantics may arise. It would be good if we could
implement these features modularly. This, however, requires that the host
language should be capable of solving the EP. Figure~\ref{code:operation} and
Figure~\ref{code:variant} together illustrate how elegant the OO solution is.
In this sense, OO languages are good candidates for defining modular EDSLs.

@@

>>>>

Before giving an example of dependent interpretations, we first show how to add new
constructs. The extended grammar of \dsl is given below,
which contains two extra constructs \emph{above} and \emph{stretch}:
\setlength{\grammarindent}{5em} % increase separation between LHS/RHS
%\lstinputlisting[linerange=39-40]{./code/shallowCircuit.hs}%APPLY:SYNTAX_TYPES
\begin{grammar}
<circuit> ::= \ldots
\alt `above' <circuit> <circuit>
\alt `stretch' <positive-numbers> <circuit>
\end{grammar}
$above\ c_1\ c_2$ combines two circuits of the same width vertically;
\emph{stretch ns c} inserts additional wires into the circuit \emph{c} by
summing up \emph{ns}.
Figure~\ref{code:variant} shows how to add new constructs - simply defining new classes that implement \lstinline{Circuit}.
\begin{figure}
\lstinputlisting[linerange=2-11]{../src/width/Variants.scala}%APPLY:VARIANT_SCALA
\caption{Adding new language constructs}
\label{code:variant}
\end{figure}

@@

\paragraph{Solving the Expression Problem (EP)} As EDSLs evolve along the time, the
demand for new syntax and new semantics may arise. It would be good if
these features can be introduced modularly. Then the capability of solving the EP
becomes a requirement of the host language.
Figure~\ref{code:operation} and Figure~\ref{code:variant} together illustrate
how elegant the OO solution,
indicating that OO languages are suitable host languages for defining modular EDSLs.
